\documentclass [8pt] {extarticle}

\usepackage {geometry}
\usepackage {multicol}

\geometry {
    a4paper,
    lmargin = 20mm,
    tmargin = 10mm,
    rmargin = 10mm,
    bmargin = 20mm,
}

\parindent=0mm

\pagestyle {empty}

\setcounter {secnumdepth} {0}

\usepackage {titlesec}
\titleformat \subsection
    {\hyphenpenalty=10000 \bf} {\thesubsection~} {0mm} {}

\begin {document}
    \section {Built-in Functions}

    \begin {multicols} {5}
        abs() \\
        aiter() \\
        all() \\
        any() \\
        anext() \\
        ascii() \\
        bin() \\
        bool() \\
        breakpoint() \\
        bytearray() \\
        bytes() \\
        callable() \\
        chr() \\
        classmethod() \\
        compile() \\
        complex() \\
        delattr() \\
        dict() \\
        dir() \\
        divmod() \\
        enumerate() \\
        eval() \\
        exec() \\
        filter() \\
        float() \\
        format() \\
        frozenset() \\
        getattr() \\
        globals() \\
        hasattr() \\
        hash() \\
        help() \\
        hex() \\
        id() \\
        input() \\
        int() \\
        isinstance() \\
        issubclass() \\
        iter() \\
        len() \\
        list() \\
        locals() \\
        map() \\
        max() \\
        memoryview() \\
        min() \\
        next() \\
        object() \\
        oct() \\
        open() \\
        ord() \\
        pow() \\
        print() \\
        property() \\
        range() \\
        repr() \\
        reversed() \\
        round() \\
        set() \\
        setattr() \\
        slice() \\
        sorted() \\
        staticmethod() \\
        str() \\
        sum() \\
        super() \\
        tuple() \\
        type() \\
        vars() \\
        zip() \\
        \_\_import\_\_() \\
    \end {multicols}

    \section {Built-in Constants}

    False \quad
    True \quad
    None \quad
    NotImplemented \quad
    Ellipsis \quad
    \_\_debug\_\_

    \section {Keywords}

    \begin {multicols} {5}
        False \\
        None \\
        True \\
        \_ (soft) \\
        and \\
        as \\
        assert \\
        async \\
        await \\
        break \\
        case (soft) \\
        class \\
        continue \\
        def \\
        del \\
        elif \\
        else \\
        except \\
        finally \\
        for \\
        from \\
        global \\
        if \\
        import \\
        in \\
        is \\
        lambda \\
        match (soft) \\
        nonlocal \\
        not \\
        or \\
        pass \\
        raise \\
        return \\
        try \\
        while \\
        with \\
        yield \\
    \end {multicols}

    \section {The standard type hierarchy}

    \begin {multicols} {3}

    None

    NotImplemented

    Ellipsis

    numbers.Number

    \quad numbers.Integral

    \qquad Integers (int)

    \qquad Booleans (bool)

    \quad numbers.Real (float)

    \quad numbers.Complex (complex)

    Sequences

    \quad Immutable sequences

    \qquad Strings

    \qquad Tuples

    \qquad Bytes

    \quad Mutable sequences

    \qquad Lists

    \qquad Byte-Arrays

    Set types

    \quad Sets

    \quad Frozen sets

    Mappings

    \quad Dictionaries

    Callable types

    \quad User-defined functions

    \quad Instance methods

    \quad Generator functions

    \quad Coroutine functions

    \quad Asynchronous generator functions

    \quad Built-in functions

    \quad Built-in methods

    \quad Classes

    \quad Class Instances

    Modules

    Custom classes

    Class instances

    I/O objects (also known as file objects)

    Internal types

    \quad Code objects

    \quad Frame objects

    \quad Traceback objects

    \quad Slice objects

    \quad Static method objects

    \quad Class method objects

    \end {multicols}

    \pagebreak

    \section {Special attributes and methods}
    

    \begin {multicols} {2}
    \subsection {User-defined functions}
    \_\_doc\_\_ \\
    \_\_name\_\_ \\
    \_\_qualname\_\_ \\
    \_\_module\_\_ \\
    \_\_defaults\_\_ \\
    \_\_code\_\_ \\
    \_\_globals\_\_ \\
    \_\_dict\_\_ \\
    \_\_closure\_\_ \\
    \_\_annotations\_\_ \\
    \_\_kwdefaults\_\_ \\

    \columnbreak

    \subsection {Modules}
    \_\_name\_\_ \quad
    \_\_doc\_\_ \quad
    \_\_file\_\_ \quad
    \_\_annotations\_\_ \quad

    \subsection {Custom classes}
    \_\_name\_\_ \\
    \_\_module\_\_ \\
    \_\_dict\_\_ \\
    \_\_bases\_\_ \\
    \_\_doc\_\_ \\
    \_\_annotations\_\_ \\
    \end {multicols}


    \begin {multicols} {2}

    \subsection {Basic customization}

    \begin {multicols} {2}
    \_\_new\_\_ \\
    \_\_init\_\_ \\
    \_\_del\_\_ \\
    \_\_repr\_\_ \\
    \_\_str\_\_ \\
    \_\_bytes\_\_ \\
    \_\_format\_\_ \\
    \_\_lt\_\_ \\
    \_\_le\_\_ \\
    \_\_eq\_\_ \\
    \_\_ne\_\_ \\
    \_\_gt\_\_ \\
    \_\_ge\_\_ \\
    \_\_hash\_\_ \\
    \_\_bool\_\_ \\
    \end {multicols}

    \subsection {Customizing attribute access}

    \_\_getattr\_\_ \\
    \_\_getattribute\_\_ \\
    \_\_setattr\_\_ \\
    \_\_delattr\_\_ \\
    \_\_dir\_\_ \\
    \_\_slots\_\_ \\

    \columnbreak

    \subsection {Customizing class creation}

    classmethod \_\_init\_subclass\_\_ \\
    \_\_set\_name\_\_ \\

    \subsection {Customizing instance and subclass checks}

    class.\_\_instancecheck\_\_ \\
    class.\_\_subclasscheck\_\_ \\

    \subsection {Emulating generic types}

    classmethod \_\_class\_getitem\_\_(cls, key)

    \subsection {Emulating callable objects}

    \_\_call\_\_(self[, args...])

    \end {multicols}

    \subsection {Emulating container types}

    \begin {multicols} {5}
    \_\_len\_\_ \\
    \_\_length\_hint\_\_ \\
    \_\_getitem\_\_ \\
    \_\_setitem\_\_ \\
    \_\_delitem\_\_ \\
    \_\_missing\_\_ \\
    \_\_iter\_\_ \\
    \_\_reversed\_\_ \\
    \_\_contains\_\_ \\
    \end {multicols}

    \subsection {Emulating numeric types}

    \begin {multicols} {5}
    \_\_add\_\_ \\
    \_\_sub\_\_ \\
    \_\_mul\_\_ \\
    \_\_matmul\_\_ \\
    \_\_truediv\_\_ \\
    \_\_floordiv\_\_ \\
    \_\_mod\_\_ \\
    \_\_divmod\_\_ \\
    \_\_pow\_\_ \\
    \_\_lshift\_\_ \\
    \_\_rshift\_\_ \\
    \_\_and\_\_ \\
    \_\_xor\_\_ \\
    \_\_or\_\_ \\
    \_\_radd\_\_ \\
    \_\_rsub\_\_ \\
    \_\_rmul\_\_ \\
    \_\_rmatmul\_\_ \\
    \_\_rtruediv\_\_ \\
    \_\_rfloordiv\_\_ \\
    \_\_rmod\_\_ \\
    \_\_rdivmod\_\_ \\
    \_\_rpow\_\_ \\
    \_\_rlshift\_\_ \\
    \_\_rrshift\_\_ \\
    \_\_rand\_\_ \\
    \_\_rxor\_\_ \\
    \_\_ror\_\_ \\
    \_\_iadd\_\_ \\
    \_\_isub\_\_ \\
    \_\_imul\_\_ \\
    \_\_imatmul\_\_ \\
    \_\_itruediv\_\_ \\
    \_\_ifloordiv\_\_ \\
    \_\_imod\_\_ \\
    \_\_ipow\_\_ \\
    \_\_ilshift\_\_ \\
    \_\_irshift\_\_ \\
    \_\_iand\_\_ \\
    \_\_ixor\_\_ \\
    \_\_ior\_\_ \\
    \_\_neg\_\_ \\
    \_\_pos\_\_ \\
    \_\_abs\_\_ \\
    \_\_invert\_\_ \\
    \_\_complex\_\_ \\
    \_\_int\_\_ \\
    \_\_float\_\_ \\
    \_\_index\_\_ \\
    \_\_round\_\_ \\
    \_\_trunc\_\_ \\
    \_\_floor\_\_ \\
    \_\_ceil\_\_ \\
    \end {multicols}

    \begin {multicols} {2}
    \subsection {With Statement Context Managers}

    \_\_enter\_\_ \\
    \_\_exit\_\_ \\

    \subsection {Customizing positional arguments in class pattern matching}

    \_\_match\_args\_\_ \\

    \subsection {Awaitable Objects}

    \_\_await\_\_ \\

    \subsection {Asynchronous Iterators}

    \_\_aiter\_\_ \\
    \_\_anext\_\_ \\

    \subsection {Asynchronous Context Managers}

    \_\_aenter\_\_ \\
    \_\_aexit\_\_ \\
    \end {multicols}

    \pagebreak

    \section {Modules}

    \begin {multicols} {5}
    abc \\
    argparse \\
    asyncio \\
    base64 \\
    calendar \\
    collections \\
    contextlib \\
    copy \\
    csv \\
    dataclasses \\
    datetime \\
    decimal \\
    enum \\
    itertools \\
    json \\
    keyword \\
    logging \\
    math \\
    numbers \\
    operator \\
    os \\
    pathlib \\
    pdb \\
    pickle \\
    pprint \\
    profile \\
    random \\
    re \\
    secrets \\
    sqlite3 \\
    statistics \\
    string \\
    sys \\
    tempfile \\
    time \\
    typing \\
    unittest \\
    urllib \\
    uuid \\
    venv \\
    zipfile \\
    \end {multicols}

    \section {Libs}

    \begin {multicols} {5}

    aiohttp \\
    alembic \\
    asgiref \\
    dateutil \\
    django \\
    djangorestframework \\
    celery \\
    coverage \\
    firebase-admin \\
    flake8 \\
    freezegun \\
    gunicorn \\
    isort \\
    more-itertools \\
    openpyxl \\
    phonenumbers \\
    pika \\
    pillow \\
    poetry \\
    psycopg2-binary \\
    pycryptodome \\
    pyfakefs \\
    pytest \\
    pytz \\
    pyyaml \\
    redis \\
    requests \\
    responses \\
    sentry-sdk \\
    sqlalchemy \\
    uWSGI \\
    validators \\

    \end {multicols}

    \section {Frameworks}

    Django \quad
    Flask \quad
    Pyramid \quad
    FastAPI \quad
    aiohttp \quad
    gevent \quad
    Tornado \quad
    Falcon \quad
    Sanic

    \section {Code analysis and refactoring}

    coverage \quad
    flake8 \quad
    isort \quad
    mypy \quad
    pylama \quad
    pylint \quad
    pyright \quad
    vulture \quad

    \pagebreak

    \section {Terms}

    \begin {multicols} {5}
        $ >>> $ \\
        ... \\
        2to3 \\
        abstract base class \\
        annotation \\
        argument \\
        asynchronous context manager \\
        asynchronous generator \\
        asynchronous generator iterator \\
        asynchronous iterable \\
        asynchronous iterator \\
        attribute \\
        awaitable \\
        BDFL \\
        binary file \\
        borrowed reference \\
        bytes-like object \\
        bytecode \\
        callback \\
        class \\
        class variable \\
        coercion \\
        complex number \\
        context manager \\
        context variable \\
        contiguous \\
        coroutine \\
        coroutine function \\
        CPython \\
        decorator \\
        descriptor \\
        dictionary \\
        dictionary comprehension \\
        dictionary view \\
        docstring \\
        duck-typing \\
        EAFP \\
        expression \\
        extension module \\
        f-string \\
        file object \\
        file-like object \\
        filesystem encoding and error handler \\
        finder \\
        floor division \\
        function \\
        function annotation \\
        \_\_future\_\_ \\
        garbage collection \\
        generator \\
        generator iterator \\
        generator expression \\
        generic function \\
        generic type \\
        GIL \\
        global interpreter lock \\
        hash-based pyc \\
        hashable \\
        IDLE \\
        immutable \\
        import path \\
        importing \\
        importer \\
        interactive \\
        interpreted \\
        interpreter shutdown \\
        iterable \\
        iterator \\
        key function \\
        keyword argument \\
        lambda \\
        LBYL \\
        locale encoding \\
        list \\
        list comprehension \\
        loader \\
        magic method \\
        mapping \\
        meta path finder \\
        metaclass \\
        method \\
        method resolution order \\
        module \\
        module spec \\
        MRO \\
        mutable \\
        named tuple \\
        namespace \\
        namespace package \\
        nested scope \\
        new-style class \\
        object \\
        package \\
        parameter \\
        path entry \\
        path entry finder \\
        path entry hook \\
        path based finder \\
        path-like object \\
        PEP \\
        portion \\
        positional argument \\
        provisional API \\
        provisional package \\
        Python 3000 \\
        Pythonic \\
        qualified name \\
        reference count \\
        regular package \\
        \_\_slots\_\_ \\
        sequence \\
        set comprehension \\
        single dispatch \\
        slice \\
        special method \\
        statement \\
        strong reference \\
        text encoding \\
        text file \\
        triple-quoted string \\
        type \\
        type alias \\
        type hint \\
        universal newlines \\
        variable annotation \\
        virtual environment \\
        virtual machine \\
        Zen of Python \\
    \end {multicols}

    \section {PEPs}

    \begin {multicols} {2}

    7  Style Guide for C Code \\
    8  Style Guide for Python Code \\
    12  Sample reStructuredText PEP Template \\
    20  The Zen of Python \\
    202  List Comprehensions \\
    203  Augmented Assignments \\
    234  Iterators \\
    249  Python Database API Specification v2.0 \\
    255  Simple Generators \\
    257  Docstring Conventions \\
    274  Dict Comprehensions \\
    279  The enumerate() built-in function \\
    282  A Logging System \\
    289  Generator Expressions \\
    308  Conditional Expressions \\
    311  Simplified Global Interpreter Lock Acquisition for ... \\
    318  Decorators for Functions and Methods \\
    327  Decimal Data Type \\
    328  Imports: Multi-Line and Absolute/Relative \\
    343  The "with" Statement \\
    345  Metadata for Python Software Packages 1.2 \\
    405  Python Virtual Environments \\
    452  API for Cryptographic Hash Functions v2.0 \\
    484  Type Hints \\
    636  Structural Pattern Matching: Tutorial \\
    3107  Function Annotations \\
    3119  Introducing Abstract Base Classes \\
    3129  Class Decorators \\
    3156  Asynchronous IO Support Rebooted: the "asyncio" Module \\
    3333  Python Web Server Gateway Interface v1.0.1 \\

    \end {multicols}

    \section {Version History}

    \begin {multicols} {3}

    \subsection {3.10}

    union types X | Y

    structural pattern matching

    parenthesized context managers

    better error messages

    TypeAlias

    loop parameter removed from most asyncio high level api

    \subsection {3.9}

    dict merge and update operators \{\} | \{\}, |=, see tricks in gallery for 25.1.22

    str.removeprefix(prefix) and str.removesuffix(suffix)

    list[str]

    new parser, based on PEG instead of LL

    new str.replace() behavior

    any valid expression can now be used as a decorator - loose decorators restrictions

    zoneinfo and graphlib modules

    typing.Annotated

    \subsection {3.8}

    assignment expressions :=

    positional-only params / *

    f-strings with '=' \{a=\}

    as\_integer\_ratio() for bool, int, Fraction

    N\{name\} in regexp

    reversed() for dict and dictview

    importlib.metadata module

    asyncio.run() in stable api

    datetime.fromisocalendar()

    \subsection {3.7}

    development mode

    new modules: contextvars, dataclasses, importlib.resources

    async, await are reserved keywords

    breakpoint(), sys.brakepointhook()

    asyncio improvements

    asyncio.get\_running\_loop()

    add nanoseconds support in time module

    await and await for in f-strings

    more than 255 function args are allowed

    str.isascii()

    datetime.fromisoformat()

    decimal uses context vars to store decimal context

    Path.is\_mount()

    sqlite3.Connection.backup()

    ZipFile compresslevel parameter

    \subsection {3.6}

    secrets module

    ...

    \subsection {3.5}

    subprocess.run()

    ...

    \end {multicols}

    \pagebreak

    \section {FAQ}

    Programming FAQ
    
    \begin {multicols} {2}

        General Questions

            Is there a source code level debugger with breakpoints, single-stepping, etc.?

            Are there tools to help find bugs or perform static analysis?

            How can I create a stand-alone binary from a Python script?

            Are there coding standards or a style guide for Python programs?

        Core Language

            Why am I getting an UnboundLocalError when the variable has a value?

            What are the rules for local and global variables in Python?

            Why do lambdas defined in a loop with different values all return the same result?

            How do I share global variables across modules?

            What are the “best practices” for using import in a module?

            Why are default values shared between objects?

            How can I pass optional or keyword parameters from one function to another?

            What is the difference between arguments and parameters?

            Why did changing list ‘y’ also change list ‘x’?

            How do I write a function with output parameters (call by reference)?

            How do you make a higher order function in Python?

            How do I copy an object in Python?

            How can I find the methods or attributes of an object?

            How can my code discover the name of an object?

            What’s up with the comma operator’s precedence?

            Is there an equivalent of C’s “?:” ternary operator?

            Is it possible to write obfuscated one-liners in Python?

            What does the slash(/) in the parameter list of a function mean?

        Numbers and strings

            How do I specify hexadecimal and octal integers?

            Why does -22 // 10 return -3?

            How do I get int literal attribute instead of SyntaxError?

            How do I convert a string to a number?

            How do I convert a number to a string?

            How do I modify a string in place?

            How do I use strings to call functions/methods?

            Is there an equivalent to Perl’s chomp() for removing trailing newlines from strings?

            Is there a scanf() or sscanf() equivalent?

            What does ‘UnicodeDecodeError’ or ‘UnicodeEncodeError’ error mean?

        Performance

            My program is too slow. How do I speed it up?

            What is the most efficient way to concatenate many strings together?

        Sequences (Tuples/Lists)

            How do I convert between tuples and lists?

            What’s a negative index?

            How do I iterate over a sequence in reverse order?

            How do you remove duplicates from a list?

            How do you remove multiple items from a list

            How do you make an array in Python?

            How do I create a multidimensional list?

            How do I apply a method to a sequence of objects?

            Why does a\_tuple[i] += [‘item’] raise an exception when the addition works?

            I want to do a complicated sort: can you do a Schwartzian Transform in Python?

            How can I sort one list by values from another list?

        Objects

            What is a class?

            What is a method?

            What is self?

            How do I check if an object is an instance of a given class or of a subclass of it?

            What is delegation?

            How do I call a method defined in a base class from a derived class that extends it?

            How can I organize my code to make it easier to change the base class?

            How do I create static class data and static class methods?

            How can I overload constructors (or methods) in Python?

            I try to use \_\_spam and I get an error about \_SomeClassName\_\_spam.

            My class defines \_\_del\_\_ but it is not called when I delete the object.

            How do I get a list of all instances of a given class?

            Why does the result of id() appear to be not unique?

            When can I rely on identity tests with the is operator?

            How can a subclass control what data is stored in an immutable instance?

            How do I cache method calls?

        Modules

            How do I create a .pyc file?

            How do I find the current module name?

            How can I have modules that mutually import each other?

            \_\_import\_\_(‘x.y.z’) returns <module ‘x’>; how do I get z?

            When I edit an imported module and reimport it, the changes don’t show up. Why does this happen?

    \end {multicols}

    Design and History FAQ

    \begin {multicols} {2}

        Why does Python use indentation for grouping of statements?

        Why am I getting strange results with simple arithmetic operations?

        Why are floating-point calculations so inaccurate?

        Why are Python strings immutable?

        Why must ‘self’ be used explicitly in method definitions and calls?

        Why can’t I use an assignment in an expression?

        Why does Python use methods for some functionality (e.g. list.index()) but functions for other (e.g. len(list))?

        Why is join() a string method instead of a list or tuple method?

        How fast are exceptions?

        Why isn’t there a switch or case statement in Python?

        Can’t you emulate threads in the interpreter instead of relying on an OS-specific thread implementation?

        Why can’t lambda expressions contain statements?

        Can Python be compiled to machine code, C or some other language?

        How does Python manage memory?

        Why doesn’t CPython use a more traditional garbage collection scheme?

        Why isn’t all memory freed when CPython exits?

        Why are there separate tuple and list data types?

        How are lists implemented in CPython?

        How are dictionaries implemented in CPython?

        Why must dictionary keys be immutable?

        Why doesn’t list.sort() return the sorted list?

        How do you specify and enforce an interface spec in Python?

        Why is there no goto?

        Why can’t raw strings (r-strings) end with a backslash?

        Why doesn’t Python have a “with” statement for attribute assignments?

        Why don’t generators support the with statement?

        Why are colons required for the if/while/def/class statements?

        Why does Python allow commas at the end of lists and tuples?
    \end {multicols}

    Library and Extension FAQ

        \begin {multicols} {2}

        Threads

            How do I program using threads?

            None of my threads seem to run: why?

            How do I parcel out work among a bunch of worker threads?

            What kinds of global value mutation are thread-safe?

            Can’t we get rid of the Global Interpreter Lock?

        Input and Output

            How do I delete a file? (And other file questions…)

            How do I copy a file?

            How do I read (or write) binary data?

        Network/Internet Programming

            How do I send mail from a Python script?

        Databases

            Are there any interfaces to database packages in Python?

            How do you implement persistent objects in Python?

        Mathematics and Numerics

            How do I generate random numbers in Python?

        \end {multicols}

\end {document}
