\documentclass [8pt] {extarticle}

\input {preamble}

\begin {document}
    \section {HTTP Methods}

    \begin {enumerate}
        \item GET
        \item HEAD
        \item POST
        \item PUT
        \item DELETE
        \item CONNECT
        \item OPTIONS
        \item TRACE
        \item PATCH
    \end {enumerate}

    \section {REST}

    \begin {enumerate}
        \item Uniform Interface
        \item Client-Server
        \item Stateless
        \item Cacheable
        \item Layered System
        \item Code on Demand (Optional)
    \end {enumerate}

    \smallskip

    Constraints to achieve a uniform interface:

    \begin {enumerate}
        \item Identification of resources
        \item Manipulation of resources through representations
        \item Self-descriptive messages
        \item Hypermedia as the engine of application state
    \end {enumerate}

    \section {SOLID}

    \begin {enumerate}
        \item The Single Responsibility Principle
        \item The Open-Closed Principle
        \item The Liskov Substitution Principle
        \item The Interface Segregation Principle
        \item The Dependency Inversion Principle
    \end {enumerate}

    \section {S.M.A.R.T.}

    \begin {enumerate}
        \item Specific
        \item Measurable
        \item Achievable
        \item Realistic
        \item Time-bound
    \end {enumerate}

    \section {The Zen of Python}

    \begin {enumerate}
        \item Beautiful is better than ugly.
        \item Explicit is better than implicit.
        \item Simple is better than complex.
        \item Complex is better than complicated.
        \item Flat is better than nested.
        \item Sparse is better than dense.
        \item Readability counts.
        \item Special cases aren't special enough to break the rules.
        \item Although practicality beats purity.
        \item Errors should never pass silently.
        \item Unless explicitly silenced.
        \item In the face of ambiguity, refuse the temptation to guess.
        \item There should be one-- and preferably only one --obvious way to do it.
        \item Although that way may not be obvious at first unless you're Dutch.
        \item Now is better than never.
        \item Although never is often better than *right* now.
        \item If the implementation is hard to explain, it's a bad idea.
        \item If the implementation is easy to explain, it may be a good idea.
        \item Namespaces are one honking great idea -- let's do more of those!
    \end {enumerate}

\end {document}
